Taming the Bitvector Bestiary

### 2024-07-26 paper.tex
Avoid redundant abstract

\begin{abstract}
% An abstract should consist of six main sentences:
%  1. Introduction. In one sentence, what’s the topic?
Bitvectors are foundational when verifying compiler backends, cryptographic
algorithms, or hardware designs.
%  2. State the problem you tackle.
Yet, they have a rich mathematical structure; in some contexts they behave as a ring,
in others as a boolean algebra,
and there is no single algebraic structure that captures the interactions between these behaviours.
This makes them hard to reason about with a uniform proof strategy.
%  3. Summarize (in one sentence) why nobody else has adequately answered the research question yet.
In the fixed-width case, the problem is well-known to be NP-complete.
Despite this, SMT solvers actually do very good job at solving these problems in practice.
% TODO: find some good explanation of why SMT solvers are not enough

%  4. Explain, in one sentence, how you tackled the research question.
We investigate different proof strategies in the Lean interactive theorem prover, 
and provide a characterization of different classes of bitvector problems, 
and which strategy will be able to solve them.

%  5. In one sentence, how did you go about doing the research that follows from your big idea.
We've collaborated closely with the Lean community to develop a canonical library for bitvectors,
including a verified bitblaster that can solve fixed-width bitvector problems.
Then, for the arbitrary-width case, we've categorized different proof strategies:
automation for commutative rings, an extensionality principle, and 
a novel finite automata-based proof strategy.

%  6. As a single sentence, what’s the key impact of your research?
By providing a characterization of different classes of bitvector problems,

\end{abstract}

@@

\input{outline/00-abstract.tex}
\input{outline/01-introduction.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}

>>>>

\begin{abstract}
\input{outline/00-abstract.tex}
\end{abstract}

@@

\input{outline/01-introduction.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}
